Holomorphic field theories and higher algebra

### 2024-08-19 draft_2022.tex
big cuts and forking

\subsection{Algebras in higher dimensions }
\label{subsec: FHK}

@@

It is easy to see
\[
{\rm Conf}_n(\CC) \cong \CC \times (\CC^\times)^{n-1}
\]
by sending a configuration $(w_1,\ldots, w_n)$ to $(w_1, w_2 - w_1, \ldots, w_n-w_{n-1})$.
(We could replace $w_1$ by any $w_j$, or even the sum of them all.)
Hence, the Dolbeault cohomology consists of holomorphic functions on this space;
there is no higher cohomology.
Inside the holomorphic functions 
\[
\cO({\rm Conf}_n(\CC)) = H^{0,*}({\rm Conf}_n(\CC)),
\] 
as a dense but understandable subalgebra, are the algebraic functions:
\[
\cO_{\rm alg}({\rm Conf}_n(\CC)) = \CC[w_1, (w_1 - w_2)^{\pm 1}, \ldots, (w_n - w_{n-1})^{\pm 1}].
\]
Here $(w_j - w_{j-1})^{\pm 1}$ means that the function $1/(w_j - w_{j-1})$ is a generator, 
as is $(w_j - w_{j-1})$.
Each such algebraic function provides an operation on $H^*(A)$, where $A$ denotes a polydisc algebra.

Let us unravel things in the special case of two points.
For simplicity, we will fix $w_1 = 0$ so that we focus on where place the other point $w_2 \in \CC^\times$.
We will use $z$ to denote this point $w_2$.
Then we have binary co-operations parametrized by $\CC[z, z^{-1}]$.
Let 
\[
V = \lim_{r \to 0} H^*(A(D_r(0)))
\]
denote the cohomological observables ``supported at the origin.''
(It would be better to take the homotopy limit of the $A(D_r(0))$,
but we leave the experienced reader to make such adjustments.)
For any two elements $a, b \in V$ and for any $n \in \ZZ$,
we then obtain an element
\[
a_{(n)} b = \int_{|z| = r} \alpha(a,b)\, z^{-n-1} \d z
\]
in $H^*(A(D_R(0))$ for any radius $R > r$.
(The choice to match $n$ with $z^{-n-1}$ is conventional.)
Any holomorphic function $f \in D_R(0) \setminus \{0\}$ also defines a map
\[
\int_{|z| = r} \alpha(a,b)\, f(z) \d z 
\]
and, if $f$ is meromorphic at the origin, then its Laurent expansion
\[
f(z) = c_{-N} z^{-N} + \cdots + c_0 + c_1 z + \cdots
\]
guarantees that we have
\[
\int_{|z| = r} \alpha(a,b)\, f(z) \d z = \sum_{n=-\infty}^{N-1} c_{-n-1} a_{(n)} b.
\]

@@

Given a Lie algebra $\lie{g}$ we obtain a one-dimensional holomorphic disc algebra $A_{\lie{g}}$ by the following construction. 
To a disk $D_r(z)$ of radius $r$ centered at $z \in \CC$ we attach the cochain complex
\beqn
A_{\lie{g}} (D_r(z)) = C_\bu \left(\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z)) \right) 
\eeqn
Here, $\Omega^{0,\bu}_c(D_r(z))$ denotes the Dolbeault complex of compactly supported $(0,\bu)$ forms on the disc.
Because the space of $(0,\bu)$ forms define a commutative dg algebra, 
the complex $\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z))$ has the natural structure of a dg Lie algebra---the complex on the right hand side is the Chevalley--Eilenberg complex which computes the Lie algebra homology of this dg Lie algebra.
Using the formalism of factorization algebras (which we recall in the next section) it is shown in \cite{CG2} how to equip $A_{\lie{g}}$ with the structure of a holomorphic disc algebra.
The corresponding vertex algebra is the Kac--Moody vertex algebra of $\fg$ at level zero. 
To obtain the vertex algebra associated to a nonzero level $\kappa$ one can deform this holomorphic polydisc algebra $A_{\fg} \rightsquigarrow A_{\fg, \kappa}$.

Let $V$ be a vector space.
Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta\gamma$ system with values in~$V$.
To a disc $D = D_r(z)$ this assigns the following cochain complex
\beqn
\Sym \left(\Omega^{1,\bu}_c(D) \otimes V^* [1] \oplus \Omega^{0,\bu}_c (D) \otimes V [1]\right) 
\eeqn
where the differential is $\dbar + \triangle$ which we will explain momentarily. 
We denote the linear generators of this symmetric algebra by $\gamma \in \Omega^{1,\bu}_c(D) \otimes V^* [1]$ and $\beta \in \Omega^{0,\bu}_c(D) \otimes V^* [1]$.
Now, for the differential, $\dbar$ is the familiar operator (which acts in the standard way on $(0,\bu)$ and $(1,\bu)$ forms) and $\triangle$ can be defined on $\Sym^2$ summand by the formula
\beqn
\triangle (\gamma \cdot \beta) = \int_D \<\gamma, \beta\> . 
\eeqn
The operator can be extended to the entire complex $A_V(D)$ by the rule that it is a BV operator for the $1$-shifted Poisson bracket given by wedge and integration.

@@

\owen{I want to mention here that we have a polydisc version}

@@

The essential idea is simple.
On a complex manifold $X$, there is a cochain map
\[
\Omega^*(X) \to \Omega^{0,*}(X)
\]
where one quotients by the dg ideal of Dolbeault $(p,q)$-forms where $p \geq 1$.
If we consider the complex manifold $\PDisc_d(r_1,\ldots,r_n|R)$, 
we get a map from its de Rham complex --- which only cares about the topology of that configuration space --- to its Dolbeault complex --- which is sensitive to its complex geometry.
Hence an algebra over the cooperad $\Omega^*(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,*}(\PDisc_d)$.
Moreover, it is straightforward (if one is comfortable with operads and higher categories) to show that 
\begin{enumerate}
\item algebras over the dg operad $C_*(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^*(\PDisc_d)$, as $\infty$-categories, and
\item $E_{2d}$-algebras are equivalent to the algebras over $C_*(\PDisc_d)$ such that an inclusion of a polydisc is always a quasi-isomorphism (the ``locally constant'' algebras).
\end{enumerate}
The second item holds because any configuration space of polydiscs is weakly equivalent, as a topological space, to the analogous configuration space of discs.
Thus we have sketched the following result.

@@

\begin{cor}
The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydiscs cooperad~$\Omega^{0,*}(\PDisc_d)$.
\end{cor}

@@

%\subsection{$E_n$ algebras from topological field theories}
%
%Although our focus in this paper is on holomorphic field theories and factorization algebras,
%it might be helpful to describe some motivating results about topological field theories and factorization algebras.
%Elliott and Safronov have \owen{not sure how much to say here, but I'm going to take a stab at writing a synoptic theorem}
%
%If one examines theories like Chern-Simons theory on $\RR^3$ or the Poisson $\sigma$-model on $\RR^2$, 
%one discovers a general format for constructing theories that was formalized by \cite{AKSZ}.
%In a nutshell, the field theory is factored into two parts: 
%the de Rham complex of the source or ``spacetime'' manifold, 
%and a Lie algebra-type object encoding a gauge Lie algebra or a ``target'' for a $\sigma$-model.
%
%\begin{dfn}
%A classical {\em AKSZ-type theory} on $\RR^d$ is a determined by an $L_\infty$-algebra $\fg$ equipped with a cyclic pairing $\langle-,-\rangle$ of degree $3-d$.
%Its {\em equation of motion} is the Maurer-Cartan equation 
%\[
%0 = \d A + \frac{1}{2} [A,A] + \frac{1}{3!}[A,A,A]_3 + \cdots = \sum_{k=1}^\infty \frac{1}{k!} [A, \ldots, A]_k
%\]
%of the $L_\infty$ algebra $\Omega^*(\RR^d) \otimes \fg$ with $k$-ary brackets $[-]_k$.
%The {\em action functional} is the expression
%\[
%S(A) = \int_{\RR^d} \sum_{k=1}^\infty \frac{1}{{k+1}!} \langle A, [A, \ldots, A]_k \rangle
%\]
%\end{dfn}
%
%Ordinary Chern-Simons theory on $\RR^3$ arises from taking $\fg$ to be a semisimple Lie algebra and a choice of invariant pairing.
%In that case, and using $\Tr$ to denote the pairing, the action functional is the familiar
%\[
%S(A) = \int_{\RR^3}  \frac{1}{2}\Tr ( A, \d A ) + \frac{1}{3!} \Tr( A, [A, A])
%\]
%and the equation of motion asks for connections with zero curvature.
%
%Many other theories can be expressed in this style, and we suggest \owen{lots of papers} for examples.
%Elliott and Safronov characterize and exhibit topological twists of supersymmetric theories as AKSZ-type theories.
%
%\begin{thm}[\cite{CG2;ElliottSafronov}]
%For a classical AKSZ-type theory on $\RR^d$, the observables 
%\[
%\Obs^{cl}(U) = \clie^*(\Omega^*(U) \otimes \fg)
%\]
%form a locally constant factorization algebra and hence determine an $E_d$ algebra~$\cA^{cl}$.
%A quantization, if it exists, determines a deformation $\cA^q$ of this $E_d$ algebra.
%
%Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
%\end{thm}

@@

\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and higher free field realization}
\label{sec: higher CDO}

@@

The class of supersymmetric theories closest to the Standard Model, however, has only $\cN=1$ supersymmetry.
There too Seiberg offered inspiring and powerful insights about SQCD ($\cN=1$ supersymmetric QCD),
and one of his leading contributions is referred to as {\em Seiberg duality}.
It has had a large impact in theoretical physics (with nearly two thousand citations),
but the impact in mathematics is much more muted,
possibly due to the lack of a topological twist for any $\cN=1$ theory.
Such theories do admit {\em holomorphic} twists, however, 
and so we explore here what holomorphic Seiberg duality might mean and what its consequences could be in mathematics.
In our opinion this direction could be quite fruitful and we welcome others to join us in exploring it.

We begin this section by describing the holomorphic twist of $\cN=1$ supersymmetric Yang--Mills theory,
and then we offer a holomorphic version of Seiberg duality, 
initially conjectured by Richard Eager.
We will point out an enrichment of this conjecture which accounts for a large symmetry enhancement that both sides of the theory enjoy after performing the holomorphic twist.
We explain our first efforts in this direction and how it offers evidence for the conjecture;
we then refine Eager's version.
We also explain how this duality, when compactified along Riemann surfaces,
should produce equivalences between different kinds of 2-dimensional B-model theories;
these reductions are related to work of Hori and Hori--Tong \cite{Hori, HorTon} and their mathematical offshoots \cite{Segal, etc}.

@@

We wish to study a holomorphic analog of supersymmetric chromodynamics.
We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
The matter fields will consist of two types: quarks and antiquarks.
Let $\underline{N}$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
so $\underline{N} = \CC^N$ with its natural left action.

@@

@@

\subsubsection{Extending the duality}

There is a way to define the dual of any supersymmetric QCD theory with mesons that satisfies the following properties:
\begin{itemize}
\item In the case that there are no mesons in the original theory, as in the electric theory, the dual agrees with the magnetic theory.
\item The dual of the magnetic theory is equivalent to the original electric theory. 
In other words, the double dual of the electric theory is equivalent to itself. 
\end{itemize}
%In fact, more generally, the double dual of any supersymmetric QCD with mesons returns the same theory (up to equivalence). 
Let us briefly remark how to state this more general duality in the holomorphic context.

Suppose that we have a holomorphic QCD theory with $N$ colors, $F$ flavors, and with mesons $\mu$ valued in some vector space $V_M$. 
The superpotential is $W(QQ^\dagger, \mu)$.
The dual theory should again be a holomorphic QCD theory with mesons:
it is holomorphic QCD with $F-N$ colors, $F$ flavors, and with mesons valued in 
\beqn
(\mu, \til \mu) \in V_M \oplus \C^{F^2} .
\eeqn
The superpotential of this dual holomorphic QCD theory (whose quarks we label by $\til Q$) is 
\beqn
\til W (\mu, \til \mu, \til Q) = W|_{\til \mu = Q Q^\dagger}(\mu, \til \mu) + \Tr \til{Q}^\dagger \til{\mu} \til{Q} .
\eeqn
Notice that when $V_M = 0, W=0$, this construction agrees with the dual magnetic theory that we introduced above.

Now, let's check how it fits with the second condition we requested. 
Start with the magnetic theory with $F-N$ colors, $F$ flavors, and $F^2$ mesons.
The superpotential is $W = \Tr(\check{Q}^\dagger \check{\mu} \check{Q})$. 
Taking the dual of this theory we obtain holomorphic QCD with $N$ colors and $F$ flavors as expected.
However, we have mesons $\check{\mu}$ and $\til \mu$, both valued in $\End(\C^F)$. 
The superpotential is simply
\beqn
\til W = \Tr( \check \mu \til \mu) + \Tr (\til Q^\dagger \check{\mu} \til Q ).
\eeqn
The first term arises from substituting $\til \mu = \check Q \check Q^\dagger$ in the original magnetic superpotential. 
This term has the effect of equipping both the mesons $\mu$ and $\check \mu$ with mass, 
and hence these fields can be integrated out to obtain the original electric theory. 
(In fact, this argument can be upgraded to give an equivalence of BV theories from the electric theory and its double dual.)

@@

As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{Whol}.
There are then two further pieces of evidence when these quantum theories are examined:
\begin{enumerate}
\item[(2)] There are {\em flavor} symmetries by $SL(F)$ that act on the quarks and antiquarks of each theory, 
and these can be matched under the duality. 
For the classical holomorphic theories, these symmetries enhance to an action of infinite-dimensional algebra of holomorphic $\sl(F)$-valued functions on the quark and antiquark fields.
Under quantization, these have isomorphic anomalies.
\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, and these can be matched under duality.
\end{enumerate}
This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
We now turn to fleshing out these assertions, but we will only discuss (1) and (2).
Aspect (1) is necessary even to formulate a precise statement,
and aspect (2) uses results --- notably the higher Kac-Moody algebras --- that we've already encountered in this survey.
Spacetime symmetries involve similar tools and ideas, albeit in a modified form, much like similarities between studying the Virasoro algebra and affine Lie algebras.

@@

Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
A {\em classical vacuum} for the theory is a solution that is translation-invariant,
i.e., a constant solution.
As the solutions $\Sol(\RR^n)$ is a derived stack (at least if you adhere to the perspective we've advocated here), there is a derived stack of classical vacua
\[
\cM_{\rm vac}(\cT) = \Sol_\cT(\RR^n)^{\RR^n}
\]
given by the substack of constant solutions.
We call it the {\em moduli stack of classical vacuum solutions} for the theory~$\cT$.

Many stacks of interest to geometers and representation theorists appear naturally from holomorphic field theories.
For example, the holomorphic $\sigma$-model from $\CC^d$ into a target complex manifold $X$ has
\[
\cM_{\rm vac} \cong T^*[1-d]X.
\]
(If we consider the underlying underived stack, it is just $X$, unless $d = 1$.)
For supersymmetric gauge theories, the moduli stack of the holomorphic twist has the form
\[
\cM_{\rm vac} \cong [V/G]
\]
where $V$ is a (graded) $G$-representation and $[V/G]$ denotes the quotient stack.
The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
the quotient by $G$ arises from the gauge transformation.
For example, the holomorphic twist of pure $\cN =1$ Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
\[
\cM_{\rm vac} \cong [\fg^*/G],
\]
the coadjoint quotient stack of the group.
(We are working in a $\ZZ/2$-graded world here.)
When $G$ is semisimple and using the invariant pairing on $\fg$, 
we can further identify this with the adjoint quotient stack~$[\fg / G]$. 
For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
\[
\cM_{\rm vac} \cong [X/G]
\]
where $X$ is a derived stack with a $G$-action and $[X/G]$ denotes the quotient stack.

>>>>

\subsection{Algebras in higher dimensions }
\label{s:alghigh}

@@

It is easy to see
\[
{\rm Conf}_n(\CC) \cong \CC \times (\CC^\times)^{n-1}
\]
by sending a configuration $(w_1,\ldots, w_n)$ to $(w_1, w_2 - w_1, \ldots, w_n-w_{n-1})$.
(We could replace $w_1$ by any $w_j$, or even the sum of them all.)
Hence, the Dolbeault cohomology consists of holomorphic functions on this space;
there is no higher cohomology.
Inside the holomorphic functions 
\[
\cO({\rm Conf}_n(\CC)) = H^{0,\bu}({\rm Conf}_n(\CC)),
\] 
as a dense but understandable subalgebra, are the algebraic functions:
\[
\cO_{\rm alg}({\rm Conf}_n(\CC)) = \CC[w_1, (w_1 - w_2)^{\pm 1}, \ldots, (w_n - w_{n-1})^{\pm 1}].
\]
Here $(w_j - w_{j-1})^{\pm 1}$ means that the function $1/(w_j - w_{j-1})$ is a generator, 
as is $(w_j - w_{j-1})$.
Each such algebraic function provides an operation on $H^*(A)$, where $A$ denotes a polydisc algebra.

Let us unravel things in the special case of two points.
For simplicity, we will fix $w_1 = 0$ so that we focus on where place the other point $w_2 \in \CC^\times$.
We will use $z$ to denote this point $w_2$.
Then we have binary co-operations parametrized by the space $\C^\times$.
Let 
\[
V = \lim_{r \to 0} H^*(A(D_r(0)))
\]
denote the cohomological observables ``supported at the origin.''
(It would be better to take the homotopy limit of the $A(D_r(0))$,
but we leave the experienced reader to make such adjustments.)
For any two elements $a, b \in V$ and for any $n \in \ZZ$,
we then obtain an element
\[
a_{(n)} b = \int_{|z| = r} \alpha(a,b)\, z^{-n-1} \d z
\]
in $H^*(A(D_R(0))$ for any radius $R > r$.
(The choice to match $n$ with $z^{-n-1}$ is conventional.)
Any holomorphic function $f \in D_R(0) \setminus \{0\}$ also defines a map
\[
\int_{|z| = r} \alpha(a,b)\, f(z) \d z 
\]
and, if $f$ is meromorphic at the origin, then its Laurent expansion
\[
f(z) = c_{-N} z^{-N} + \cdots + c_0 + c_1 z + \cdots
\]
guarantees that we have
\[
\int_{|z| = r} \alpha(a,b)\, f(z) \d z = \sum_{n=-\infty}^{N-1} c_{-n-1} a_{(n)} b.
\]

@@

Given a Lie algebra $\lie{g}$ we obtain a one-dimensional holomorphic disc algebra $A_{\lie{g}}$ by the following construction. 
To a disk $D_r(z)$ of radius $r$ centered at $z \in \CC$ we attach the cochain complex
\beqn
\label{eqn:diskskm}
A^{\lie{g}} (D_r(z)) = C_\bu \left(\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z)) \right) 
\eeqn
Here, $\Omega^{0,\bu}_c(D_r(z))$ denotes the Dolbeault complex of compactly supported $(0,\bu)$ forms on the disc.
Because the space of $(0,\bu)$ forms define a commutative dg algebra, 
the complex $\lie{g} \otimes \Omega^{0,\bu}_c(D_r(z))$ has the natural structure of a dg Lie algebra---the complex on the right hand side is the Chevalley--Eilenberg complex which computes the Lie algebra homology of this dg Lie algebra.
Using the formalism of factorization algebras (which we recall in the next section) it is shown in \cite{CG2} how to equip $A_{\lie{g}}$ with the structure of a holomorphic disc algebra.
The corresponding vertex algebra is the Kac--Moody vertex algebra of $\fg$ at level zero. 
To obtain the vertex algebra associated to a nonzero level $\kappa$ one can deform this holomorphic polydisc algebra $A^{\fg} \rightsquigarrow A^\fg_{\kappa}$.

Let $V$ be a vector space.
Then, we can define a holomorphic disc algebra $A_V$ which corresponds to another familiar vertex algebra: the $\beta-\gamma$ system with values in~$V$.
To a disc $D = D_r(z)$ this assigns the following cochain complex
\beqn
\Sym \left(\Omega^{1,\bu}_c(D) \otimes V^* [1] \oplus \Omega^{0,\bu}_c (D) \otimes V [1]\right) 
\eeqn
where the differential is $\dbar + \triangle$ which we will explain momentarily. 
We denote the linear generators of this symmetric algebra by $\gamma \in \Omega^{1,\bu}_c(D) \otimes V^* [1]$ and $\beta \in \Omega^{0,\bu}_c(D) \otimes V^* [1]$.
Now, for the differential, $\dbar$ is the familiar operator (which acts in the standard way on $(0,\bu)$ and $(1,\bu)$ forms) and $\triangle$ can be defined on $\Sym^2$ summand by the formula
\beqn
\triangle (\gamma \cdot \beta) = \int_D \<\gamma, \beta\> . 
\eeqn
The operator can be extended to the entire complex $A_V(D)$ by the rule that it is a BV operator for the $1$-shifted Poisson bracket given by wedge and integration.
The vertex algebra associated to this disk algebra is the familiar $\beta-\gamma$-vertex algebra.

@@

It is apparent that the formula in \eqref{eqn:diskskm} makes sense for a (poly)disk of arbitrary complex dimension $d$.
In this way, we obtain functor from Lie algebras to $d$-polydisks algebras $\fg \mapsto A^{\fg}_d$.
(Here $A^{\fg}_1 = A^{\fg}$.)

In this section we have mostly focused on disks.
If we evaluate $A^{\lie{g}}_{d}$ on a punctured disk rather than a disk then we obtain a complex which receives a dense embedding from the complex
\beqn
\Sym \left(\lie{g}^\bu_{d}\right) 
\eeqn
where $\lie{g}^\bu_d$ is the higher sphere algebra from Definition \ref{dfn:sphere}.
A natural question is how the Lie algebra structure appears; to address this we will use the language of factorization algebras in the next section.

Given an invariant polynomial $\theta \in \Sym^{d+1}(\lie{g}^*)^G$ as in \S \ref{s:alghigh} we can obtain a twisted version of this $d$-polydisks algebra $A^{\lie{g}}_{d,\theta}$.
At the level of the punctured disk this corresponds to the higher Kac--Moody algebra which is the central extension of the sphere algebra $\lie{\fg}^\bu_{d}$.
This is a $d$-polydisks avatar of the higher Kac--Moody algebra, in the same way that the Kac--Moody vertex algebra is related to the affine Kac--Moody Lie algebra \cite{GWkm}.

@@

The essential idea is simple.
On a complex manifold $X$, there is a cochain map
\[
\Omega^\bu(X) \to \Omega^{0,\bu}(X)
\]
where one quotients by the dg ideal of Dolbeault $(p,q)$-forms where $p \geq 1$.
If we consider the complex manifold $\PDisc_d(r_1,\ldots,r_n|R)$, 
we get a map from its de Rham complex --- which only cares about the topology of that configuration space --- to its Dolbeault complex --- which is sensitive to its complex geometry.
Hence an algebra over the cooperad $\Omega^\bu(\PDisc_d)$ forgets to an algebra over the cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
Moreover, it is straightforward (if one is comfortable with operads and higher categories) to show that 
\begin{enumerate}
\item algebras over the dg operad $C_\bu(\PDisc_d)$ are equivalent to algebras over the dg cooperad~$\Omega^\bu(\PDisc_d)$, as $\infty$-categories, and
\item $E_{2d}$-algebras are equivalent to the algebras over $C_\bu(\PDisc_d)$ such that an inclusion of a polydisc is always a quasi-isomorphism (the ``locally constant'' algebras).
\end{enumerate}
The second item holds because any configuration space of polydiscs is weakly equivalent, as a topological space, to the analogous configuration space of discs.
Thus we have sketched the following result.

@@

\begin{cor}
The observables of a topological field theory on $\RR^{2d}$ determine an algebra over the polydiscs cooperad~$\Omega^{0,\bu}(\PDisc_d)$.
\end{cor}

@@

%\subsection{$E_n$ algebras from topological field theories}
%
%Although our focus in this paper is on holomorphic field theories and factorization algebras,
%it might be helpful to describe some motivating results about topological field theories and factorization algebras.
%Elliott and Safronov have \owen{not sure how much to say here, but I'm going to take a stab at writing a synoptic theorem}
%
%If one examines theories like Chern-Simons theory on $\RR^3$ or the Poisson $\sigma$-model on $\RR^2$, 
%one discovers a general format for constructing theories that was formalized by \cite{AKSZ}.
%In a nutshell, the field theory is factored into two parts: 
%the de Rham complex of the source or ``spacetime'' manifold, 
%and a Lie algebra-type object encoding a gauge Lie algebra or a ``target'' for a $\sigma$-model.
%
%\begin{dfn}
%A classical {\em AKSZ-type theory} on $\RR^d$ is a determined by an $L_\infty$-algebra $\fg$ equipped with a cyclic pairing $\langle-,-\rangle$ of degree $3-d$.
%Its {\em equation of motion} is the Maurer-Cartan equation 
%\[
%0 = \d A + \frac{1}{2} [A,A] + \frac{1}{3!}[A,A,A]_3 + \cdots = \sum_{k=1}^\infty \frac{1}{k!} [A, \ldots, A]_k
%\]
%of the $L_\infty$ algebra $\Omega^\bu(\RR^d) \otimes \fg$ with $k$-ary brackets $[-]_k$.
%The {\em action functional} is the expression
%\[
%S(A) = \int_{\RR^d} \sum_{k=1}^\infty \frac{1}{{k+1}!} \langle A, [A, \ldots, A]_k \rangle
%\]
%\end{dfn}
%
%Ordinary Chern-Simons theory on $\RR^3$ arises from taking $\fg$ to be a semisimple Lie algebra and a choice of invariant pairing.
%In that case, and using $\Tr$ to denote the pairing, the action functional is the familiar
%\[
%S(A) = \int_{\RR^3}  \frac{1}{2}\Tr ( A, \d A ) + \frac{1}{3!} \Tr( A, [A, A])
%\]
%and the equation of motion asks for connections with zero curvature.
%
%Many other theories can be expressed in this style, and we suggest \owen{lots of papers} for examples.
%Elliott and Safronov characterize and exhibit topological twists of supersymmetric theories as AKSZ-type theories.
%
%\begin{thm}[\cite{CG2;ElliottSafronov}]
%For a classical AKSZ-type theory on $\RR^d$, the observables 
%\[
%\Obs^{cl}(U) = \clie^*(\Omega^\bu(U) \otimes \fg)
%\]
%form a locally constant factorization algebra and hence determine an $E_d$ algebra~$\cA^{cl}$.
%A quantization, if it exists, determines a deformation $\cA^q$ of this $E_d$ algebra.
%
%Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
%\end{thm}

@@

\section{Holomorphic $\sigma$-models, higher algebras of differential operators, and higher free field realization}

@@

The class of supersymmetric theories closest to the Standard Model, however, has only $\cN=1$ supersymmetry.
There too Seiberg offered inspiring and powerful insights about SQCD ($\cN=1$ supersymmetric QCD),
and one of his leading contributions is referred to as {\em Seiberg duality}.
It has had a large impact in theoretical physics \owen{give the citation number on that paper},
but the impact in mathematics is much more muted,
possibly due to the lack of a topological twist for any $\cN=1$ theory.
Such theories do admit {\em holomorphic} twists, however, 
and so we explore here what holomorphic Seiberg duality might mean and what its consequences could be in mathematics.
In our opinion this direction could be quite fruitful and we welcome others to join us in exploring it.

We begin this section by describing the holomorphic twist of $\cN=1$ supersymmetric Yang--Mills theory,
and then we offer a holomorphic version of Seiberg duality, 
initially conjectured by Richard Eager.
We will point out an enrichment of this conjecture which accounts for a large symmetry enhancement that both sides of the theory enjoy after performing the holomorphic twist.
We explain our first efforts in this direction and how it offers evidence for the conjecture;
we then refine Eager's version.
We also explain how this duality, when compactified along Riemann surfaces,
should produce equivalences between different kinds of 2-dimensional B-model theories;
these reductions are related to work of Hori and Hori--Tong \owen{citations} and its mathematical development by Ed Segal, \owen{list others}.

@@

We wish to study a holomorphic analog of supersymmetric chromodynamics.
We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
The matter fields will consist of two types: quarks and antiquarks.
Let $\underline{N}$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
so $\underline{N} = \CC^N$ with its natural left action.
\owen{That's kind of crappy notation. Let's discuss.}
\brian{Does it help us much? Or are you trying to use this to disambiguate what $\CC^N$ means.}

@@

\owen{Do we want $F > N+1$? The physicists break things into several cases. In particular, I think the moduli is unchanged under quantization only if $F$ is big enough relative to $N$ and $\check{N}$.}
\brian{I expect we want a similar condition, but I was never able to understand how that appears at the level of factorization algebras.}

@@

\subsubsection{The duality functor}

There is a way to define the dual of any supersymmetric QCD theory with mesons that satisfies the following properties:
\begin{itemize}
\item In the case that there are no mesons in the original theory, like in the electric theory, the dual agrees with the magnetic theory.
\item The dual of the magnetic theory is equivalent to the original electric theory. In other words, the double dual of the electric theory is equivalent to itself. 
\end{itemize}
%In fact, more generally, the double dual of any supersymmetric QCD with mesons returns the same theory (up to equivalence). 
Let us briefly remark how this general duality looks classically in the holomorphic context.

Suppose that we have a holomorphic QCD theory with $N$ colors, $F$ flavors, and with mesons $\mu$ valued in some vector space $V_M$. 
The superpotential is $W(QQ^\dagger, \mu)$.
The dual theory is again a holomorphic QCD theory with mesons.
Precisely the dual theory is holomorphic QCD with $F-N$ colors, $F$ flavors, and mesons valued in 
\beqn
(\mu, \til \mu) \in V_M \oplus \C^{F^2} .
\eeqn
The superpotential of this dual holomorphic QCD theory (whose quarks we label by $\til Q$) is 
\beqn
\til W (\mu, \til \mu, \til Q) = W|_{\til \mu = Q Q^\dagger}(\mu, \til \mu) + \Tr \til{Q}^\dagger \til{\mu} \til{Q} .
\eeqn
Notice that when $V_M = 0, W=0$ this agrees with the dual magnetic theory that we introduced above.

Now, let's suppose we start with the magnetic theory with $F-N$ colors, $F$ flavors, and $F^2$ mesons.
The superpotential is $W = \Tr \check{Q}^\dagger \check{\mu} \check{Q}$. 
Taking the dual of this theory we obtain holomorphic QCD with $N$ colors and $F$ flavors as expected.
However, we have mesons $\check{\mu}$ and $\til \mu$ both valued in $\End(\C^F)$. 
The superpotential is simply
\beqn
\til W = \Tr \check \mu \til \mu + \Tr \til Q^\dagger \check{\mu} \til Q .
\eeqn
The first term arises from substituting $\til \mu = \check Q \check Q^\dagger$ in the original magnetic superpotential. 
This term has the effect of making both $\mu,\check \mu$ massive, and hence they can be integrated out to obtain the original electric theory. 
(In fact, this argument can be upgraded to give an equivalence of BV theories from the electric theory and its double dual.)

@@

As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{Whol}.
There are then two further pieces of evidence when these quantum theories are examined:
\begin{enumerate}
\item[(2)] There are {\em flavor} symmetries by $SL(F)$ that act on the quarks and antiquarks of each theory, 
and these can be matched under the duality. 
For the classical holomorphic theories, these symmetries enhance to an action of infinite-dimensional algebra of holomorphic $\sl(F)$-valued functions on the quark and antiquark fields.
Under quantization, these have isomorphic anomalies.
\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, and these can be matched under duality.
\end{enumerate}
This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
We now turn to fleshing out these assertions.

@@

Now such a field theory $\cT$ on $\RR^n$ has a space of solutions $\Sol_\cT(\RR^n)$ to its equations of motion.
A {\em classical vacuum} for the theory is a solution that is translation-invariant,
i.e., a constant solution.
As the solutions $\Sol(\RR^n)$ is a derived stack (at least if you adhere to the perspective we've advocated here), there is a derived stack of classical vacua
\[
\cM_{\rm vac}(\cT) = \Sol_\cT(\RR^n)^{\RR^n}
\]
given by the substack of constant solutions.
We call it the {\em moduli stack of classical vacua} for the theory~$\cT$.

Many stacks of interest to geometers and representation theorists appear naturally from holomorphic field theories.
For example, the holomorphic $\sigma$-model from $\CC^d$ into a target complex manifold $X$ has
\[
\cM_{\rm vac} \cong T^*[1-d]X.
\]
(If we consider the underlying underived stack, it is just $X$, unless $d = 1$.)
For supersymmetric gauge theories, the moduli stack of the holomorphic twist has the form
\[
\cM_{\rm vac} \cong [V/G]
\]
where $V$ is a (graded) $G$-representation and $[V/G]$ denotes the quotient stack.
The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
the quotient by $G$ arises from the gauge transformation.
For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
\[
\cM_{\rm vac} \cong [\fg^*/G],
\]
the coadjoint quotient stack of the group.
\brian{The paragraph began with holomorphic theories, do you want to say twist of 4d N=1?}
(We are working in a $\ZZ/2$-graded world here.)
Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$[\fg / G]$. 
For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
\[
\cM_{\rm vac} \cong [X/G]
\]
where $X$ is a derived stack with a $G$-action and $[X/G]$ denotes the quotient stack.
